\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Machine Learning Club}
\author{ML Club Officers}
\date{September 13, 2017}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}

\begin{document}

\maketitle

\section{Introduction}
Machine Learning Club is an organization where members can learn the theory and applications of machine learning, test their skills in intra-club contests and online competitions, and conduct machine learning research. We meet every Wednesday A Block in Room 202.

\section{Officers}
\begin{itemize}
    \item Captain: Mihir Patel
    \item Captain: Nikhil Sardana
    \item Teaching Coordinator: Justin Zhang
    \item Teaching Coordinator: Sylesh Suresh
\end{itemize}

Contact the club officers through Facebook Messenger (preferred) or at \texttt{tjmachinelearning@gmail.com}.

\section{Lectures}

Lectures will begin with standard machine learning topics before delving into deep learning. We cover not only classical machine learning and deep learning algorithms, but also new and exciting advances. As research comes out throughout the year, we will periodically discuss any interesting developments. 

The following lecture schedule is the current plan for the school year. The lecture schedule is subject to change, and the most up to date version can always be found at \texttt{tjmachinelearning.com/schedule}.

\begin{tabular}{|r|l| }
  \hline
\textbf{Date} & \textbf{Lecture} \\
  \hline
9/13/17 & Introduction to Machine Learning \\ 
9/20/17 & Decision Trees and Random Forests \\ 
9/27/17 & Naive Bayes \\ 
10/4/17 & SVMs \\ 
10/11/17 & k-Nearest neighbors \\ 
10/18/17 & Neural Networks 1 \\ 
10/25/17 & Neural Networks 2: Vectorization \\ 
11/1/17 & Neural Networks 3: Optimizations \\ 
11/8/17 & Intro to TF, Keras, PyTorch \\ 
11/15/17 & CNNs: Intro \\ 
11/22/17 & Deep Nets and Transfer Learning \\ 
11/29/17 & Working with Special Image Data \\ 
12/6/17 & Segmentation \\ 
12/13/17 & Object Detection \\ 
12/20/17 & Winter Break \\ 
12/27/17 & Winter Break \\ 
1/3/18 & Undetermined CNN Lecture \\ 
1/10/18 & intro to RNNs + LSTM/GRU \\ 
1/17/18 & Intro to NLP \\ 
1/24/18 &Newer RNNs \\ 
1/31/18 &Machine Translation+Linguistics \\ 
2/7/18 &Time-Series Data: Audio \\ 
2/14/18 &Intro to GANs \\ 
2/21/18 &Newer GANs \\ 
2/28/18 & PixelCNN and PixelRNN \\ 
3/7/18 & Autoencoders and Markov Chains \\ 
3/14/18 & Intro to RL and Gym \\ 
3/21/18 & Deep Reinforcement Learning \\ 
3/28/18 & Spring Break \\ 
4/4/18 & Human-in-the-loop RL \\ 
4/11 - 5/30 & Guest Lectures, Kaggle Competition, ML Research \\ 
6/6/18 & Elections \\
  \hline
\end{tabular}

\section{Quizzes and Exams}
Quizzes and exams will be given occasionally to ensure students learn and retain material. These, along with the In-House contests (see Section 5.1) will be used to rank students.

\section{Competitions}
\subsection{In-House Contests}
Machine Learning Club will be holding weekly in-house contests through Kaggle Classroom. Details on the specifics of Kaggle Classroom will be given alongisde the first contest. Unless otherwise specified, contests will begin on Wednesday evening after Machine Learning Club and run until 11:59:00 P.M. on the following Monday. Students will be ranked based on their achievement in these contests.

\subsection{Outside Competitions}
As the year progresses, Machine Learning Club members can participate in Kaggle competitions (\texttt{kaggle.com/competitions}). Substantial prize money is awarded to winners of contests, however, students will be competiting against anyone in the entire world, so the probability of winning is extremely low. Nevertheless, Kaggle competitions are a valuable learning experience.

\section{Research}
Machine Learning Club is formalizing its research initiative. This year, anyone who is having trouble with an ML research problem, wants input on the feasibility and/or scope of potential projects, or is looking for general ML help can ask the officers and receive help during club time. The current officers have experience at the highest level of high school research. After the lecture schedule ends in April, students will have more time to work on research projects, applying the knowledge from the lectures to real-world data.

\section{The Website}
Most information is conveyed through the official Machine Learning Club website, \texttt{tjmachinelearning.com}. Here, you can find the lectures in pdf and web form, along with any presentations, notes, rankings, or additional resources.

\section{First Day Form}
Go to \texttt{tjmachinelearning.com} and click "Join Us Today" on your phone or computer. Fill out the form.

\end{document}
